***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2015-10-12 Schloss_Cluster_PeerJ_2015.Rmd
Remove slow steps from Rmd file

```{r, cache=TRUE}
gg_summary <- read.table(file="data/gg_13_8/gg_13_8_97.v19.summary", header=T)
n_v4_overlap <- sum(gg_summary$start <= 3967 & gg_summary$end >= 6116)
n_v9_overlap <- sum(gg_summary$start <= 10179 & gg_summary$end >= 10683)

@@

```{r, cache=TRUE}
v4_dist <- read.table(file="data/gg_13_8/gg_13_8_97.v4_ref.unique.dist")
n_small_v4_dist <- sum(v4_dist$V3<=0.03)

v19_dist <- read.table(file="data/gg_13_8/gg_13_8_97.v19_ref.unique.dist")
n_small_v19_dist <- sum(v19_dist$V3<=0.03)

v19_summary <- read.table(file="data/gg_13_8/gg_13_8_97.v19.summary", header=T)

n_v4_unique <- length(scan("data/gg_13_8/gg_13_8_97.v4_ref.names", what="", sep="\n", quiet=T))

>>>>

```{r, cache=TRUE}
n_overlap <- read.table(file="data/gg_13_8/gg_13_8_97.overlap.count", row.names=1)
n_v4_overlap <- n_overlap["v4", 1]
n_v9_overlap <- n_overlap["v9", 1]

@@

```{r, cache=TRUE}
small_dists <- read.table(file="data/gg_13_8/gg_13_8_97.small_dist.count", row.names=1)
n_small_v4_dist <- small_dists["v4",1]
n_small_v19_dist <- small_dists["v19",1]

n_v4_unique <- length(scan(file="data/gg_13_8/gg_13_8_97.v4_ref.names", what="", sep="\n", quiet=T))
